A Deeper Look into Bug Fixes: Patterns, Replacements, Deletions, and Additions

### 2016-03-14 MSRChallenge2016.tex
acknowledgements, plus some spacing

\subsection{Detection Approach}
Because direct diffs are difficult to identify on this dataset, we heuristically approximate the
extent to which one statement type appears to be ``replaced'' by another.
For each modified file, we count the number of
appearances of each statement type in the file pre- and post-commit.  We then
compare the results to see how many of each statement type was removed, and how
many inserted, to roughly characterize the types of replacement that happen at a
per-file level.
%   For each statement type (as tagged by the Boa infrastructure
% for Java), we process the results as follows: if number of occurrences of one
% statement type decreased post-fix and the number of another type increased, we
% say that the first statement type was replaced by the second statement type for
% that file. 
Note that this analysis doesn't distinguish the
replacement of the same statement kind, since we are counting the amount of
appearances of each statement kind.
%
We follow a similar approach to approximately count deletions and
insertions. 
For each bug fixing revision $r$ and each statement kind $k$, we compare the
count of statements of kind $k$ in revision $r$ and $r-1$.

\subsection{Results}

\noindent\textbf{Potential replacements.} Table~\ref{tab:likeliness} shows
the replacement likelihood for our dataset 
(each cell shows the percent of the time that the statement in the \emph{row}
was replaced by a statement of the type in the \emph{column}). For example, 
the corresponding to the $\mathtt{Do}$ row (row 5) and $\mathtt{Assert}$ column (column 2)
shows 0.81, indicating that $\mathtt{Do}$ statements were
replaced by $\mathtt{Assert}$ statements 0.81\% of the times.

@@

>>>>

\vspace{1ex}
\noindent\textbf{Detection Approach}
Because direct diffs are difficult to identify on this dataset, we heuristically approximate the
extent to which one statement type appears to be ``replaced'' by another.
For each modified file, we count the number of
appearances of each statement type in the file pre- and post-commit.  We then
compare the results to see how many of each statement type was removed, and how
many inserted, to roughly characterize the types of replacement that happen at a
per-file level.
%   For each statement type (as tagged by the Boa infrastructure
% for Java), we process the results as follows: if number of occurrences of one
% statement type decreased post-fix and the number of another type increased, we
% say that the first statement type was replaced by the second statement type for
% that file. 
Note that this analysis doesn't distinguish the
replacement of the same statement kind, since we are counting the amount of
appearances of each statement kind.
%
We follow a similar approach to approximately count deletions and
insertions. 
For each bug fixing revision $r$ and each statement kind $k$, we compare the
count of statements of kind $k$ in revision $r$ and $r-1$.

\vspace{1ex}
\noindent\textbf{Potential replacements.} Table~\ref{tab:likeliness} shows
the replacement likelihood for our dataset 
(each cell shows the percent of the time that the statement in the \emph{row}
was replaced by a statement of the type in the \emph{column}). For example, 
the corresponding to the $\mathtt{Do}$ row (row 5) and $\mathtt{Assert}$ column (column 2)
shows 0.81, indicating that $\mathtt{Do}$ statements were
replaced by $\mathtt{Assert}$ statements 0.81\% of the times.

@@

\section{Acknowledgements}

This work is partially supported by the US Department of Defense through the
Systems Engineering Research Center (SERC), Contract H98230-08-D-0171.
